\documentclass{article}
    % HEADER
    % Packages to use

    \usepackage{latexsym}
    \usepackage[empty]{fullpage}
    \usepackage{titlesec}
    \usepackage{marvosym}
    \usepackage[usenames,dvipsnames]{color}
    \usepackage{verbatim}
    \usepackage{enumitem}
    \usepackage[hidelinks]{hyperref}
    \usepackage{fancyhdr}
    \usepackage[default]{lato}
    \usepackage[T1]{fontenc}
    \usepackage{multicol}
    \usepackage{geometry}
    % Set paper and margin size
    \geometry{paper=letterpaper, top=15mm, left=18mm, right=18mm, bottom=20mm}

    % Set header text and sizing
    \fancyhf{}
    \fancyhead[L]{C. Maxwell Reilly} \fancyhead[C]{cmaxreilly.github.io} \fancyhead[R]{Page Two}
    \pagestyle{fancy}
    \thispagestyle{empty}

    \renewcommand{\headrulewidth}{0pt}
    \renewcommand{\footrulewidth}{0pt}

    \urlstyle{same}

    \raggedbottom
    % I don't see this section above mattering very much, since my goal is a
    % one page cv and these changes only apply to the header on page 2...

    % Sections formatting
    \titleformat{\section}{
        \centering \vspace{-4pt} \large
    } {} {0em}\textbf{}

    \titleformat{\subsection}{
        \vspace{-4pt} \large
    } {} {0em}\textbf{}

    % ---------- Custom commands ----------
    \newcommand{\cvItem}[1]{
        \item {
            {#1}
        }
    }
    % Subheading with one title
    \newcommand{\cvSubheading}[4]{
        \vspace{-1pt}\item[]
            \begin{tabular*}{1\textwidth}[t]{l@{\extracolsep{\fill}}r}
                \textbf{#1} #2 & \textbf{#3} \\
                \textbf{#4}\\
            \end{tabular*}\vspace{-5pt}
    }
    \newcommand{\cvSubHeadingListStart}{\begin{itemize}[leftmargin=0pt]}
    \newcommand{\cvSubHeadingListEnd}{\end{itemize}}
    \newcommand{\cvItemListStart}{\begin{itemize}[leftmargin=10pt]}
    \newcommand{\cvItemListEnd}{\end{itemize}}
    \newcommand{\cvEducationSubheading}[2]{
        \vspace{-1pt}\item[]
            \begin{tabular*}{1\textwidth}[t]{l@{\extracolsep{\fill}}r}
                \textbf{#1} \\
                {#2} \\
            \end{tabular*}
    }


% ---------- CV Starts Here ----------
\begin{document}
    % ---------- HEADING ----------
    % Centered heading with name, location, and contact info
    \begin{center}
        \textbf{\Large C. Maxwell Reilly} \\ Albuquerque NM 87104
        \href{mailto:c.maxwell.reilly@gmail.com}{c.maxwell.reilly@gmail.com}
    \end{center}\vspace{-11pt}
    % Space for phone number and website link below header
    \begin{center}
        \begin{tabular}{c c}
            (970) 620-0975 & \href{https://cmaxreilly.github.io}{cmaxreilly.github.io} \\
        \end{tabular}\vspace{-8pt}
    \end{center}
    % HR divider
    \rule{\textwidth}{1pt}

    % ---------- Education ----------
    \section{EDUCATION}
        \cvSubHeadingListStart
            \cvEducationSubheading
                {Bachelor of Music, Keyboard Performance}
                {Colorado Mesa University, Grand Junction, CO}
            \cvEducationSubheading
                {Work toward Bachelor of Music, Piano Performance}
                {University of Denver, Denver, CO}
        \cvSubHeadingListEnd

    % ---------- Principal Teachers ----------
    \section{PRINCIPAL TEACHERS}
        \cvItemListStart
            \begin{multicols}{2}
                \cvItem{Stephanie Shih-Yu Cheng - 2015-2017}
                \cvItem{Marjorie Zollner - 2019-2020}
                \cvItem{Gisela Flanigan - 2020-2021, 2023-2025} 
                \cvItem{Brian Krinke - 2021-2024}
                \cvItem{Darin Kamstra - 2021-2022}
                \cvItem{Adrian Herrera-Escobar - 2021-2023}
            \end{multicols}
        \cvItemListEnd

    % ---------- Masterclasses ----------
    \section{MASTERCLASSES}
        \cvItem{Alan Broadbent}
        \cvItem{Alexandra Nguyen}

    % ---------- Chamber music coaches ----------
    \section{CHAMBER MUSIC COACHES}
        \cvItemListStart
            \begin{multicols}{3}
                \cvItem{Jason Pegis}
                \cvItem{Basil Vandreyes}
                \cvItem{Matthew Plenk}
                \cvItem{Laura Husbands}
                \cvItem{Jun Watabe}
                \cvItem{Roberto Arundale}
                \cvItem{Timothy Emmons}
            \end{multicols}
        \cvItemListEnd

    % ---------- Experience ----------
    \section{WORK EXPERIENCE}
        \cvSubHeadingListStart
            \cvSubheading
            {COLORADO MESA UNIVERSITY,} {Grand Junction, CO}{August 2022 - May 2025}
            {Adjunct Faculty, Resident Accompanist}
                \cvItemListStart
                    \cvItem
                        {Accompanied and music-directed musicals and classes for theater department.}
                    \cvItem
                        {Accompanied classes, lessons, and several student recitals a semester for the
                        music department.}
                    \cvItem
                        {Taught private piano lessons and worked as a vocal coach out
                        of office on campus.}
                    \cvItem
                        {Collaborated with music and theater faculty on performances and policy.}
                \cvItemListEnd

            \cvSubheading
            {GRAND JUNCTION HIGH SCHOOL,}{Grand Junction, CO} {August 2018 - May 2025}
            {Choir Accompanist}
                \cvItemListStart
                    \cvItem
                        {Accompanied for classes, concerts and recitals for Grand Junction High
                        school.}
                    \cvItem
                        {Created improvised accompaniments in collaboration with teachers and
                        students, in styles including jazz, baroque, classical, and contemporary
                        commercial.}
                    \cvItem
                        {Played piano for musicals for the first three years there, and wrote the
                        underscoring to the drama department's production of \textit{Treasure
                        Island} by Ken Ludwig.}
                \cvItemListEnd

            \cvSubheading
            {FIRST PRESBYTERIAN CHURCH,}{Grand Junction, CO}{August 2023 - June 2025}
            {Pianist, Organist}
                \cvItemListStart
                    \cvItem
                        {Principally accompanied for the choir on organ and piano in weekly
                        rehearsal, service, and concerts under the baton of David Sherman.}
                    \cvItem
                        {Served as substitute organist and pianist for hymn playing during service}
                    \cvItem
                        {Played keyboards and planned worship with the commercial band for special
                        services}
                \cvItemListEnd
        \cvSubHeadingListEnd

    \section{PERFORMANCE HIGHLIGHTS}
        \subsection{2025}
            \cvItemListStart
                \cvItem{Accompanied Jeremy Franklin's Farewell concert after his 18 year career as
                the head of the CMU musical theater department}
                \cvItem{{\em Little Noon Music} performed a solo recital of masterworks, originals,
                and improvisation}
                \cvItem{Music director for the Colorado Mesa University Theater Department's
                production of {\em Ride the Cyclone} in the Asteria Theater}
                \cvItem{Recital with international artist Naama Liany at the Pitkin County Library,
                as a part of their concert series.}
                \cvItem{{\em Impromptu} composer concert. Played original works and works by
                composer Julie McCarthy}
            \cvItemListEnd
        \subsection{2024}
            \cvItemListStart
                \cvItem{Music director for Geek Parties' production of {\em Cannibal the Musical} at
                the Avalon Theater in Grand Junction Colorado}
                \cvItem{Soprano Rainy Stokely-Graves Junior Recital in Love Recital Hall at CMU}
                \cvItem{Accompanied Kurt Kowar cello recital under the coaching of Roberto Arundale
                at the Basalt Regional Library}
                \cvItem{Accompanied Nicholas Berry's Senior Cello Recital in Love Recital Hall at
                CMU}
                \cvItem{Accompanied Emily Larsen's Senior Cello Recital in Love Recital Hall at CMU}
                \cvItem{Music director for \& Company's production of {\em Chicago}}
                \cvItem{Performed the role of Wolfgang Amadeus Mozart in the CMU theater
                department's production of {\em Amadeus} for the grand opening of the Asteria
                Theater in Grand Junction, CO under the direction of Mo LaMee. Wrote, improvised, or
                learned all music performed onstage}
                \cvItem{Performed and original piece on the CMU Music Faculty Gala in the Asteria
                Theater}
                \cvItem{Played Piano for the CMU Theater Department's production of {\em
                Urinetown}.}
                \cvItem{Transcribed and arranged Scottish and Irish folk songs for Dr. Chris McKim and
                Dr. Caitlin Moore's faculty recital {\em Celtic Impressions}. Assisted with
                rehearsals.}
                \cvItem{Accompanied Scott Betts' recital for {\em Little Noon Music} at First United
                Methodist Church}
            \cvItemListEnd
        \subsection{2023}
            \cvItemListStart
                \cvItem{Played piano for High Desert Opera's production of {\em Always Patsy Cline}
                at the Avalon Theater in Grand Junction CO.}
                \cvItem{Accompanied the District 51 Middle School Honor Choir under the direction of
                Brad Hirsh}
                \cvItem{Accompanied Indiana Jones' senior recital in Love Recital hall under the
                coaching of Jason Pegis}
                \cvItem{Played piano for the world premier of Scott Betts' musical {\em Eclipse} at
                the Avalon Theater in Grand Junction CO.}
                \cvItem{Accompanied the Valley Symphony Association's Choir for their {\em Young
                Composers, Be Inspired!} concert.}
                \cvItem{Wrote the underscoring for Grand Junction High School's production of Ken
                Ludwig's {\em Treasure Island} with Brad Hirsh}
                \cvItem{Played piano for the CMU Theater Department's production of {\em Floyd
                Collins} under the direction of Mo LaMee and music direction of Jeremy Franklin.
                Also served as technical consultant on audio effects.}
                \cvItem{Accompanied Valley Symphony Associations concert {\em Pop Stars and
                Superheroes.}}
                \cvItem{Played piano for the Knights Templar Christmas Observance}
            \cvItemListEnd
        \subsection{2022}
            \cvItemListStart
                \cvItem{Accompanied {\em Christmas by Candelight} concert for the Valley Symphony
                Orchestra Chorus}
                \cvItem{Accompanied the Grand Junction High School Solo Voice Recital.}
                \cvItem{Performed a solo recital of masterworks, arrangments, and originals for my
                Senior Recital in Love Recital Hall at CMU.}
                \cvItem{Performed with Matt Harris at the CMU Jazz concert in Robinson theater}
                \cvItem{Perfomed and original arrangment of {\em Veni, Emmanuel} for the First
                United Methodist Christmas concert.}
                \cvItem{Played piano for Grand Junction High School's production of {\em High School
                Musical}. Used Ableton Live for sample automation, sound design, and some
                composition.}
            \cvItemListEnd
        \subsection{2021}
            \cvItemListStart
                \cvItem{Accompanied Shayna Lindblom's Senior Clarinet Recital in Love Recital Hall
                at Colorado Mesa University under the coaching of Jun Watabe.}
            \cvItemListEnd
        \subsection{2020}
            \cvItemListStart
                \cvItem{Played piano for Grand Junction High School's production of {\em Little Shop
                of Horrors}.}
            \cvItemListEnd
        \subsection{2019}
        \subsection{2018}
        \subsection{2017}
        \subsection{2016}


\end{document}
