\documentclass{article}
    % HEADER
    % Packages to use

    \usepackage{latexsym}
    \usepackage[empty]{fullpage}
    \usepackage{titlesec}
    \usepackage{marvosym}
    \usepackage[usenames,dvipsnames]{color}
    \usepackage{verbatim}
    \usepackage{enumitem}
    \usepackage[hidelinks]{hyperref}
    \usepackage{fancyhdr}
    \usepackage[default]{lato}
    \usepackage[T1]{fontenc}
    \usepackage{multicol}
    \usepackage{geometry}
    % Set paper and margin size
    \geometry{paper=letterpaper, top=15mm, left=18mm, right=18mm, bottom=20mm}

    % Set header text and sizing
    \fancyhf{}
    \fancyhead[L]{C. Maxwell Reilly} \fancyhead[C]{cmaxreilly.github.io} \fancyhead[R]{Page Two}
    \pagestyle{fancy}
    \thispagestyle{empty}

    \renewcommand{\headrulewidth}{0pt}
    \renewcommand{\footrulewidth}{0pt}

    \urlstyle{same}

    \raggedbottom
    % I don't see this section above mattering very much, since my goal is a
    % one page resume and these changes only apply to the header on page 2...

    % Sections formatting
    \titleformat{\section}{
        \centering \vspace{-4pt} \large
    } {} {0em}\textbf{}

    % ---------- Custom commands ----------
    \newcommand{\resumeItem}[1]{
        \item{
            {#1}
        }
    }
    % Subheading with one title
    \newcommand{\resumeSubheading}[4]{
        \vspace{-1pt}\item[]
            \begin{tabular*}{1\textwidth}[t]{l@{\extracolsep{\fill}}r}
                \textbf{#1} #2 & \textbf{#3} \\
                \textbf{#4}\\
            \end{tabular*}\vspace{-5pt}
    }
    \newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0pt]}
    \newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
    \newcommand{\resumeItemListStart}{\begin{itemize}[leftmargin=10pt]}
    \newcommand{\resumeItemListEnd}{\end{itemize}}
    \newcommand{\resumeEducationSubheading}[2]{
        \vspace{-1pt}\item[]
            \begin{tabular*}{1\textwidth}[t]{l@{\extracolsep{\fill}}r}
                \textbf{#1} \\
                {#2} \\
            \end{tabular*}
    }


% ---------- Resume Starts Here ----------
\begin{document}
    % ---------- HEADING ----------
    % Centered heading with name, location, and contact info
    \begin{center}
        \textbf{\Large C. Maxwell Reilly} \\ Albuquerque NM 87104
        \href{mailto:c.maxwell.reilly@gmail.com}{c.maxwell.reilly@gmail.com}
    \end{center}\vspace{-11pt}
    % Space for phone number and website link below header
    \begin{center}
        \begin{tabular}{c c}
            (970) 620-0975 & \href{https://cmaxreilly.github.io}{cmaxreilly.github.io} \\
        \end{tabular}\vspace{-8pt}
    \end{center}
    % HR divider
    \rule{\textwidth}{1pt}

    % ---------- Profile ----------
    \section{PROFESSIONAL PIANIST}
        \resumeSubHeadingListStart
            \item []
                Accomplished and versatile pianist skilled at
                collaboration, interpretation, improvisation, and
                composition. Passionate and thoughtful artist, interested
                in music in all of its forms. Excellent communication
                skills with a solid background in performance, theory,
                teaching, and technology.
        \resumeSubHeadingListEnd

    % ---------- Education ----------
    \section{EDUCATION}
        \resumeSubHeadingListStart
            \resumeEducationSubheading
                {Bachelor of Music, Keyboard Performance}
                {Colorado Mesa University, Grand Junction, CO}
            \resumeEducationSubheading
                {Work toward Bachelor of Music, Piano Performance}
                {University of Denver, Denver, CO}
        \resumeSubHeadingListEnd

    % ---------- Experience ----------
    \section{EXPERIENCE}
        \resumeSubHeadingListStart
            \resumeSubheading
            {COLORADO MESA UNIVERSITY,} {Grand Junction, CO}{August 2022 - May 2025}
            {Adjunct Faculty, Resident Accompanist}
                \resumeItemListStart
                    \resumeItem
                        {Accompanied and music-directed musicals and classes for theater department.}
                    \resumeItem
                        {Accompanied classes, lessons, and several student recitals a semester for the
                        music department.}
                    \resumeItem
                        {Taught private piano lessons and worked as a vocal coach out
                        of office on campus.}
                    \resumeItem
                        {Collaborated with music and theater faculty on performances and policy.}
                \resumeItemListEnd

            \resumeSubheading
            {GRAND JUNCTION HIGH SCHOOL,}{Grand Junction, CO} {August 2018 - May 2025}
            {Choir Accompanist}
                \resumeItemListStart
                    \resumeItem
                        {Accompanied for classes, concerts and recitals for Grand Junction High
                        school.}
                    \resumeItem
                        {Created improvised accompaniments in collaboration with teachers and
                        students, in styles including jazz, baroque, classical, and contemporary
                        commercial.}
                    \resumeItem
                        {Played piano for musicals for the first three years there, and wrote the
                        underscoring to the drama department's production of \textit{Treasure
                        Island} by Ken Ludwig.}
                \resumeItemListEnd

            \resumeSubheading
            {FIRST PRESBYTERIAN CHURCH,}{Grand Junction, CO}{August 2023 - June 2025}
            {Pianist, Organist}
                \resumeItemListStart
                    \resumeItem
                        {Principally accompanied for the choir on organ and piano in weekly
                        rehearsal, service, and concerts under the baton of David Sherman.}
                    \resumeItem
                        {Served as substitute organist and pianist for hymn playing during service}
                    \resumeItem
                        {Played keyboards and planned worship with the commercial band for special
                        services}
                \resumeItemListEnd

            \resumeSubheading
            {FREELANCE MUSICIAN,}{Grand Junction, CO}{August 2017 - Present}
            {Recitalist, Keyboardist, Composer, Educator}
                \resumeItemListStart
                    \resumeItem
                        {Played classical recitals from Grand Junction to Denver}
                    \resumeItem
                        {Recording artist and/or producer on dozens of publicly available songs by
                        western slope artists}
                    \resumeItem
                        {Scored original music and arrangements for recitals and theater productions.}
                    \resumeItem
                        {Taught private lessons and served as a clinician to University and private studios.}
                \resumeItemListEnd
        \resumeSubHeadingListEnd

    % ---------- Skills ----------
    \newpage
    \vspace*{10pt}
    \section{MUSICAL SKILLS}
        % Bulleted multi-column list of skills
        \begin{multicols}{3}
            \begin{itemize}[leftmargin=10pt]
                \item Classical Interpretation
                \item Collaborative Piano
                \item Musical Theater
                \item Contemporary Commercial Music
                \item Jazz Improvisation
                \item Composition
                \item Songwriting
                \item Arranging
                \item Pedagogy
            \end{itemize}
        \end{multicols}

    \section{SPECIAL SKILLS}
        \begin{multicols}{3}
            \begin{itemize}[leftmargin=10pt]
                \item Acting
                \item Computer Programming
                \item Writing
            \end{itemize}
        \end{multicols}
    % ---------- Technical Proficiencies ----------
    \section{TECHNICAL PROFICIENCIES}
        \resumeSubHeadingListStart
            \item[]
                \textbf{Composition Software}{: Sibelius, Finale, Musescore, Lilypond}
            \item[]
                \textbf{Audio Software}{: Pro-Tools, Logic, Reaper, Ableton}
            \item[]
                \textbf{Programming/Scripting Languages}{: C, Python, Bash, Javascript, Lua}
            \item[]
                \textbf{Technologies}{: Linux, Git, Github, HTML/CSS}
        \resumeSubHeadingListEnd


\end{document}
