\documentclass{article}
    % HEADER
    % Packages to use

    \usepackage{latexsym}
    \usepackage[empty]{fullpage}
    \usepackage{titlesec}
    \usepackage{marvosym}
    \usepackage[usenames,dvipsnames]{color}
    \usepackage{verbatim}
    \usepackage{enumitem}
    \usepackage[hidelinks]{hyperref}
    \usepackage{fancyhdr}
    \usepackage[default]{lato}
    \usepackage[T1]{fontenc}
    \usepackage{multicol}
    \usepackage{geometry}
    % Set paper and margin size and page numbering.
    \geometry{paper=letterpaper, top=15mm, left=18mm, right=18mm, bottom=20mm}


    % Set header text and sizing

    \renewcommand{\headrulewidth}{0pt}
    \renewcommand{\footrulewidth}{0pt}

    \urlstyle{same}

    \raggedbottom
    % I don't see this section above mattering very much, since my goal is a
    % one page cv and these changes only apply to the header on page 2...

    % Added page numbers
    \pagestyle{fancy}
    \fancyhf{}
    \fancyfoot[C]{\thepage}

    % Sections formatting
    \titleformat{\section}{
        \centering \vspace{-4pt} \large
    } {} {0em}\textbf{}

    \titleformat{\subsection}{
        \vspace{-4pt} \large
    } {} {0em}\textbf{}

    % Formatting multicols
    \setlength{\multicolsep}{0pt}

    % ---------- Custom commands ----------
    \newcommand{\cvItem}[1]{
        \item {
            {#1}
        }
    }
    % Subheading with one title
    \newcommand{\cvSubheading}[4]{
        \vspace{-1pt}\item[]
            \begin{tabular*}{1\textwidth}[t]{l@{\extracolsep{\fill}}r}
                \textbf{#1} #2 & \textbf{#3} \\
                \textbf{#4}\\
            \end{tabular*}\vspace{-5pt}
    }
    \newcommand{\cvSubHeadingListStart}{\begin{itemize}[leftmargin=0pt]}
    \newcommand{\cvSubHeadingListEnd}{\end{itemize}}
    \newcommand{\cvItemListStart}{\begin{itemize}[leftmargin=10pt]}
    \newcommand{\cvItemListEnd}{\end{itemize}}
    \newcommand{\cvEducationSubheading}[3]{
        \vspace{-1pt}\item[]
            \begin{tabular*}{1\textwidth}[t]{l@{\extracolsep{\fill}}r}
                \textbf{#1} \\ % Name of the Degree
                {#2} % City Name
                { --- \em #3} \\ % Years attended and notes
            \end{tabular*}
    }


% ---------- CV Starts Here ----------
\begin{document}
    \pagenumbering{arabic}
    \setcounter{page}{1}
    % ---------- HEADING ----------
    % Centered heading with name, location, and contact info
    \begin{center}
        \textbf{\Large C. Maxwell Reilly} \\ Albuquerque NM \hspace{2mm}
        \href{mailto:c.maxwell.reilly@gmail.com}{c.maxwell.reilly@gmail.com}
    \end{center}\vspace{-11pt}
    % Space for phone number and website link below header
    \begin{center}
        \begin{tabular}{c c}
            (970) 620-0975 \\
        \end{tabular}\vspace{-8pt}
    \end{center}
    % HR divider
    \rule{\textwidth}{1pt}

    % ---------- Education ----------
    \section{EDUCATION}
        \cvSubHeadingListStart
            \cvEducationSubheading
                {Bachelor of Music, Keyboard Performance}
                {Colorado Mesa University, Grand Junction, CO}
                {Final institution. Degree awarded spring of 2022}
            \cvEducationSubheading
                {Bachelor of Music, Piano Performance}
                {University of Denver, Denver, CO}
                {Coursework completed: 2015-2018}
        \cvSubHeadingListEnd

    % ---------- Principal Teachers ----------
    \section{PRINCIPAL PIANO TEACHERS}
        \cvItemListStart
            \begin{multicols}{2}
                \cvItem{Stephanie Shih-Yu Cheng - 2015-2018}
                \cvItem{Marjorie Zollner - 2019-2020}
                \cvItem{Gisela Flanigan - 2020-2021, 2023-2025}
                \cvItem{Adrian Herrera-Escobar - 2021-2023}
            \end{multicols}
        \cvItemListEnd

    % ---------- Masterclasses ----------
    \section{MASTERCLASSES}
        \cvItemListStart
            \begin{multicols}{2}
                \cvItem{Alan Broadbent}
                \cvItem{Alexandra Nguyen}
            \end{multicols}
        \cvItemListEnd

    % ---------- Chamber music coaches ----------
    \section{CHAMBER MUSIC COACHES}
        \cvItemListStart
            \begin{multicols}{3}
                \cvItem{Jason Pegis}
                \cvItem{Basil Vandreyes}
                \cvItem{Matthew Plenk}
                \cvItem{Laura Husbands}
                \cvItem{Jun Watabe}
                \cvItem{Roberto Arundale}
                \cvItem{Timothy Emmons}
                \cvItem{Caitlin Moore}
                \cvItem{Sean Flanigan}
            \end{multicols}
        \cvItemListEnd

    % ---------- Experience ----------
    \section{WORK EXPERIENCE}
        \cvSubHeadingListStart
            \cvSubheading
            {COLORADO MESA UNIVERSITY,} {Grand Junction, CO}{August 2022 - May 2025}
            {Adjunct Faculty, Resident Accompanist}
                \cvItemListStart
                    \cvItem
                        {Accompanied and music-directed musicals and classes for theater department.}
                    \cvItem
                        {Accompanied classes, lessons, and several student recitals per semester for
                        the music department.}
                    \cvItem
                        {Taught private piano lessons and worked as a vocal coach.}
                    \cvItem
                        {Collaborated with music and theater faculty on performances and policy.}
                \cvItemListEnd

            \cvSubheading
            {GRAND JUNCTION HIGH SCHOOL,}{Grand Junction, CO} {August 2018 - May 2025}
            {Choir Accompanist}
                \cvItemListStart
                    \cvItem
                        {Accompanied for classes, concerts and recitals for Grand Junction High
                        school.}
                    \cvItem
                        {Created improvised accompaniments in collaboration with teachers and
                        students, in styles including jazz, baroque, classical, and contemporary
                        commercial.}
                    \cvItem
                        {Played piano for musicals, and wrote the underscoring to the drama
                        department's production of \textit{Treasure Island} by Ken Ludwig.}
                    \cvItem
                        {Served as a substitute teacher for choir classes.}
                    \cvItem
                        {Accompanied solos for yearly solo and ensemble festival, and other district
                        51 related solo performances.}
                \cvItemListEnd
            \pagebreak
            \cvSubheading
            {FIRST PRESBYTERIAN CHURCH,}{Grand Junction, CO}{August 2023 - June 2025}
            {Pianist, Organist}
                \cvItemListStart
                    \cvItem
                        {Accompanied for the choir on organ and piano in weekly rehearsal, service,
                        and concerts under the baton of Dr. David Sherman.}
                    \cvItem
                        {Served as substitute organist and pianist during services.}
                    \cvItem
                        {Played keyboards and planned worship with the commercial band for special
                        services.}
                \cvItemListEnd
            \cvSubheading
            {VALLEY SYMPHONY ASSOCIATION CHORUS,}{Delta and Montrose, CO}{November 2022 - April
            2023}{Choral Accompanist}
                \cvItemListStart
                    \cvItem
                        {Accompanied for choral rehearsals in Delta, Colorado.}
                    \cvItem
                        {Accompanied and improvised accompaniment for choral and orchestral concerts
                        in Montrose, Colorado.}
                    \cvItem
                        {Prepared digital accompaniments for rehearsals and concerts.}
                \cvItemListEnd
            \cvSubheading
            {FIRST CONGREGATIONAL UNITED CHURCH OF CHRIST,}{Grand Junction, CO}{February 2020 -
            August 2023}{Pianist, Organist}
                \cvItemListStart
                    \cvItem
                        {Accompanied all congregational song, choral music, and soloists on piano
                        and organ.}
                    \cvItem
                        {Prepared, composed, or improvised solo preludes, postludes, and interludes
                        for services and special concerts.}
                    \cvItem
                        {Digitally recorded and edited video and audio for service music during
                        COVID-19 pandemic lockdown.}
                \cvItemListEnd
            \cvSubheading
            {DISTRICT 51,}{Grand Junction, CO}{August 2018 - May 2025}{Choral Accompanist, Composer,
            Consultant}
                \cvItemListStart
                    \cvItem
                        {Accompanied choirs at West Middle School.}
                    \cvItem
                        {Accompanied choirs for Juniper Ridge Waldorf School.}
                    \cvItem
                        {Served as a sound reinforcement consultant for Colorado West Music
                        Festival.}
                    \cvItem
                        {Served as a music substitute for various schools.}
                    \cvItem
                        {Recorded digital accompaniments and tracks for various performances and
                        rehearsals.}
                \cvItemListEnd
            \cvSubheading
            {WESTMINSTER CHRISTIAN CHURCH,}{Westminster, CO}{September 2015 - March 2018}{Pianist,
            Organist}
                \cvItemListStart
                    \cvItem
                        {Accompanied all congregational song, choral music, and soloists on piano
                        and organ.}
                    \cvItem
                        {Prepared, composed, or improvised solo preludes, postludes, and interludes
                        for services and special concerts.}
                    \cvItem
                        {Assisted in talent aquisition of section leaders.}
                \cvItemListEnd
            {DENVER WALDORF SCHOOL,}{Denver, CO}{September 2017 - March 2018}{Choral Accompanist}
                \cvItemListStart
                    \cvItem
                        {Accompanied choral rehearsals and performances.}
                    \cvItem
                        {Accompanied for and coached students on solos performances.}
                \cvItemListEnd
        \cvSubHeadingListEnd
    \section{PERFORMANCE HIGHLIGHTS}
        \subsection{2025}
            \cvItemListStart
                \cvItem{Accompanied Jeremy Franklin's farewell concert after his 18 year career as
                the head of the CMU musical theater department.}
                \cvItem{{\em Little Noon Music} performed a solo recital of masterworks, originals,
                and improvisation.}
                \cvItem{Music director for the Colorado Mesa University Theater Department's
                production of {\em Ride the Cyclone} in the Asteria Theater under the direction of
                Jeremy Franklin.}
                \cvItem{Recital with international artist Naama Liany at the Pitkin County Library,
                as a part of their concert series.}
                \cvItem{{\em Impromptu} composer concert. Played original works and works by
                composer Julie McCarthy.}
                \cvItem{Clarinet recital with John Petefish at Canvas 35.}
                \cvItem{Karli Weatherill senior flute recital in Love Recital Hall.}
                \cvItem{Bonnie Duffy senior voice recital under the coaching of Caitlin Moore.}
                \cvItem{Accompanied several top students at the Colorado \& Wyoming NATS at
                University of Denver.}
                \cvItem{Accompanied John Petefish's senior clarinet recital in Love Recital hall
                under the coaching of Jun Watabe.}
                \cvItem{Played piano, organ, and harpsichord for the Easter concert with First
                Presbyterian.}
                \cvItem{Played jazz piano with Doug Ferony and the Clark Gault Dectet at the
                Mizel Foundation fundraiser in Denver Colorado. Attendees included Colorado
                Governers Jared Polis and Bill Rittner, as well as hundreds of business and political
                dignitaries from Colorado.}
            \cvItemListEnd
        \subsection{2024}
            \cvItemListStart
                \cvItem{Music director for Geek Parties' production of {\em Cannibal the Musical} at
                the Avalon Theater in Grand Junction Colorado.}
                \cvItem{Soprano Rainy Stokely-Graves Junior Recital in Love Recital Hall at CMU.}
                \cvItem{Accompanied Kurt Kowar cello recital under the coaching of Roberto Arundale
                at the Basalt Regional Library.}
                \cvItem{Accompanied Nicholas Berry's Senior Cello Recital in Love Recital Hall at
                CMU.}
                \cvItem{Accompanied Emily Larsen's Senior Cello Recital in Love Recital Hall at CMU.}
                \cvItem{Music director for \& Company's production of {\em Chicago}.}
                \cvItem{Performed the role of Wolfgang Amadeus Mozart in the CMU theater
                department's production of {\em Amadeus} for the grand opening of the Asteria
                Theater in Grand Junction, CO under the direction of Mo LaMee. Wrote, improvised, or
                learned all music performed onstage, and was featured in several articles in the GJ
                Sentinal.}
                \cvItem{Performed and original piece on the CMU Music Faculty Gala in the Asteria
                Theater.}
                \cvItem{Played Piano for the CMU Theater Department's production of {\em
                Urinetown}.}
                \cvItem{Transcribed and arranged Scottish and Irish folk songs for Dr. Chris McKim and
                Dr. Caitlin Moore's faculty recital {\em Celtic Impressions}. Assisted with
                rehearsals.}
                \cvItem{Accompanied Scott Betts' recital for {\em Little Noon Music} at First United
                Methodist Church.}
                \cvItem{Headlined Mesa Theater in Grand Junction Colorado with band {\em Kid
                Caravan}.}
            \cvItemListEnd
        \subsection{2023}
            \cvItemListStart
                \cvItem{Headlined Mesa Theater in Grand Junction Colorado with band {\em Kid
                Caravan}.}
                \cvItem{Played piano for the CMU Theater Department's production of {\em Floyd
                Collins} under the direction of Mo LaMee and music direction of Jeremy Franklin.
                Also served as technical consultant on audio effects.}
                \cvItem{Wrote the underscoring for Grand Junction High School's production of Ken
                Ludwig's {\em Treasure Island} with Brad Hirsh.}
                \cvItem{Played piano for the world premier of Scott Betts' musical {\em Eclipse} at
                the Avalon Theater in Grand Junction CO.}
                \cvItem{Played piano for High Desert Opera's production of {\em Always Patsy Cline}
                at the Avalon Theater in Grand Junction CO.}
                \cvItem{Accompanied Indiana Jones' senior cello recital in Love Recital hall under
                the coaching of Jason Pegis.}
                \cvItem{Accompanied several placing students at the Colorado \& Wyoming NATS at
                University of Northern Colorado.}
                \cvItem{Accompanied the Valley Symphony Association's Choir for their {\em Young
                Composers, Be Inspired!} concert.}
                \cvItem{Accompanied Valley Symphony Associations concert {\em Pop Stars and
                Superheroes.}}
                \cvItem{Accompanied the District 51 Middle School Honor Choir under the direction of
                Brad Hirsh.}
                \cvItem{Played piano for the Knights Templar Christmas Observance.}
                \cvItem{Personal band {\em Late Night Five} rebranded as {\em Kid Caravan} selected
                to open for {\em Baby Jake} and {\em Bryce Vine} at the CMU Spring Concert.}
            \cvItemListEnd
        \subsection{2022}
            \cvItemListStart
                \cvItem{Rehearsal accompanist for CMU's production of {\em Guys and Dolls}.}
                \cvItem{Accompanied {\em Christmas by Candelight} concert for the Valley Symphony
                Orchestra Chorus.}
                \cvItem{Accompanied the Grand Junction High School Solo Voice Recital.}
                \cvItem{Performed a solo recital of masterworks, arrangments, and originals for my
                Senior Recital in Love Recital Hall at CMU.}
                \cvItem{Performed with Jazz Pianist Matt Harris at the CMU Jazz concert in Robinson
                theater.}
                \cvItem{Perfomed and original arrangment of {\em Veni, Emmanuel} for the First
                United Methodist Christmas concert.}
                \cvItem{Played piano for Grand Junction High School's production of {\em High School
                Musical}. Used Ableton Live for sample automation, sound design, and composition.}
                \cvItem{Only music student selected to represent the music department in CMU
                president John Marshall's presentation to the Colorado State Senate Capital
                Development Committee. Performed a short work with a vocalist from the Theater
                Department.}
                \cvItem{Started band {\em Late Night Five} with fellow students, winning a
                university battle of the bands a few days later.}
                \cvItem{Performed in drum ensemble {\em Talking Rhythmns} for CMU Prism Concert.}
            \cvItemListEnd
        \subsection{2021}
            \cvItemListStart
                \cvItem{Peformed a solo stride piano arrangment of {\em All of Me} for the CMU Prism
                Concert. Was the only student selected to play a solo.}
                \cvItem{Accompanied Shayna Lindblom's Senior Clarinet Recital in Love Recital Hall
                at Colorado Mesa University under the coaching of Jun Watabe.}
            \cvItemListEnd
        \subsection{2020}
            \cvItemListStart
                \cvItem{Played piano for Grand Junction High School's production of {\em Little Shop
                of Horrors}.}
                % Something about that gig I did in Texas with Darcy here, if I ever find the name,
                % lol.
            \cvItemListEnd
        \subsection{2019}
            \cvItemListStart
                \cvItem{Pianist for Grand Junction High School's production of {\em Into the
                Woods}.}
            \cvItemListEnd
        \subsection{2018}
            \cvItemListStart
                \cvItem{Jazz Piano for Clark Gault Dectet at Grand Junction VA Hospital for
                Veteran's Day.}
                \cvItem{Student accompanist for Liederabend II for diction class at DU under the guidance
                of Matthew Plenk and Hukum Singh Khalsa.}
                \cvItem{Pianist for D'Evelyn High School's production of {\em Big Fish} in Denver, CO.}
            \cvItemListEnd
        \subsection{2017}
            \cvItemListStart
                \cvItem{Student Accompanist for Liederabend I for diction class at DU under the guidance
                of Matthew Plenk and Hukum Singh Khalsa.}
            \cvItemListEnd
        \subsection{2016}
            \cvItemListStart
                \cvItem{Played piano for the world premiere of Kevin Padworski's {\em The Cloud}.}
            \cvItemListEnd
        \newpage

    \section{OTHER PRIVATE STUDY}
        \cvItemListStart
            \begin{multicols}{2}
                \cvItem{Voice: Marcia Kuhlman}
                \cvItem{Voice: Kelly Anderson}
                \cvItem{Organ: Dr. Joseph Galema}
                \cvItem{Organ: Dr. John Howard}
                \cvItem{Bass: Timothy Emmons}
                \cvItem{Improvisation and Composition: Jon Cowherd}
                \cvItem{Improvisation and Composition: Dr. Darin Kamstra}
                \cvItem{Composition, Ear Training: Brian Krinke}
            \end{multicols}
        \cvItemListEnd
    \section{CHORAL HIGHLIGHTS}
       \cvItemListStart
           \cvItem{2017: Sang tenor in Berlioz's {\em The Damnation of Faust} with the Colorado
           Symphony Orchestra chorus at the Aspen Music Festival.}
           \cvItem{2016: Sang tenor in Orff's {\em Carmina Burana} with the Colorado Symphony
           Orchestra Chorus at the Aspen Music Festival and for Bravo Vail.}
        \cvItemListEnd


\end{document}
